%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% abstract.tex: Abstract
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Maria -- I think the abstract has to be just one page, but I am not sure
% TRO
Swarm Robotics is the study of the coordination of large numbers of simple
robots. In this thesis, we develop new mathematical tools and models to aid in
the design of swarm-robotic systems, and provide at least partial answers to
four important open research questions in the field.

First:~\glsdesc{RQ1} We present a set of metrics intended to
supplement designer intuitions when designing swarm-robotic systems, increase
accuracy in extrapolating swarm behavior from algorithmic descriptions and small
test experiments, and lead to faster and less costly design cycles. We build on
previous works studying self-organizing behaviors in autonomous systems to
derive a metric for swarm emergent self-organization.  We utilize techniques
from high performance computing, time series analysis, and queueing theory to
derive metrics for swarm scalability, flexibility to changing external
environments, and robustness to internal system stimuli such as sensor and
actuator noise and robot failures.  We demonstrate the utility of our metrics by
analyzing four different control algorithms in an indoor warehouse object
transport scenario with static objects and a spatially unconstrained outdoor
search and rescue scenario with moving objects. We show that our intuitions
about comparative algorithm performance are well supported by the quantitative
results obtained using our metrics, and that our metrics can be synergistically
used together to predict collective behaviors based on previous results in some
cases.

% AAMAS

Second:~\glsdesc{RQ2} We use task allocation within the context of task
decomposition graphs of different cross-clique centralities, and derive two
different allocation methods to answer this question. First, a self-organized
task allocation algorithm designed to be sensitive to clique centrality.
Second, a greedy algorithm that optimally solves the swarm task allocation
problem under some restrictive assumptions by representing the swarm's task
allocation space as a matroid. We compare the greedy allocation method, which
disregards task dependencies, with the clique-sensitive method, which emphasizes
collective learning of graph structure (including dependencies), with other
state of the art algorithms. Results from an object gathering task show that
swarm emergent intelligence (1) is sensitive to cross-clique centrality of task
decomposition graphs (2) is positively correlated with performance, (3) arises
out of learning and exploitation of graph connectivity and structure, rather
than graph content.

% ODE/AR

Third:~\glsdesc{RQ3} We study the limits of linear modeling of swarm behavior by
characterizing the inflection point beyond which linear models of swarm
collective behavior break down. We design a linear model which strives to
capture the underlying dynamics of object gathering in robot swarms from first
principles, rather than extensively relying on post-hoc model fitting.  We
evaluate our model with swarms of up to \num{8,000} robots in simulation,
demonstrating that it accurately captures underlying swarm behavioral dynamics
when the swarm can be approximated using the mean-field model, and when it
cannot, and finite-size effects are present.  We further apply our model to
swarms exhibiting non-linear behaviors, and show that it still provides accurate
predictions in some scenarios, thereby establishing better practical limits on
linear modeling of swarm behaviors.

Fourth:~\glsdesc{RQ4} We investigate the conditions under which such bounds can
be obtained in the context of graph manipulation tasks in which robots can
add/remove nodes/edges from a graph as they manipulate elements of their
environment. We present a novel graph theoretic description of a class of graphs
describing discrete 3D structures which can be concurrently manipulated by an
arbitrary number of robots to achieve a desired system goal. We demonstrate the
flexibility of our approach with several simple construction and deconstruction
tasks using heterogeneous blocks, and discuss implications for the design of
future multi-robot systems using this approach to tackle important real-world
problems such as construction, farming, and repair of critical infrastructure
such as roads and levies after a disaster.
