%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% acknowledge.tex: Acknowledgements
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

First and foremost, I have to thanks my research supervisor, Dr. Maria Gini of
the Computer Science Department at the University of Minnesota. Her door was
always open whenever I got stuck in research, or needed feedback about my
academic writing. She consistently pushed me to make this thesis my own work,
but steered me in the right direction whenever she thought I needed it. Your
insightful feedback pushed me to sharpen my thinking and brought my work to a
higher level.

I would like to thank the University of Minnesota MnDRIVE and UMII programs for
providing funding opportunities for my research without which I would not have
been able to ......

I would like to thank my labmates and grad school colleagues for providing
invaluable feedback on my writing and research. I would particularly like to
single out Libby Ferland for her invaluable copy editing skills in polishing my
papers, and Carrie Miller for her willingness to read and provide feedback on
every single draft of many of my papers.

------ other stuff?

Finally, I would like to express my very profound gratitude to my parents and to
my partner for providing unfailing, unflagging, continuous encouragement and
support throughout my years of study and through the process of writing this
thesis. This accomplishment would not have been possible without them. Thank
you.

% Maria -  no need for your name since it is in your thesis
John Harwell -- Am I supposed to put my name at the end of the acknowledgements? --

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
