%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Research Question Definitions
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newglossaryentry{RQ1}
{
  %
  name={\textbf{RQ1}},
  %
  description={can the observable properties of emergent
      self-organization, scalability, flexibility, and robustness of robot
      swarms be measured quantitatively?}  }

\newglossaryentry{RQ2}
{
  %
  name={\textbf{RQ2}},
  %
  description={where does emergent intelligence come from in a robot swarm?}
}

\newglossaryentry{RQ2.1}
{
  %
  name={\textbf{RQ2.1}},
  %
  description={do \emph{complex} task decomposition graphs result in
      greater swarm emergent intelligence than \emph{compound} graphs?}
}

\newglossaryentry{RQ2.2}
{
  %
  name={\textbf{RQ2.2}},
  %
  description={is the emergence of swarm intelligence within task
        decomposition graphs a function of the graph connectivity, or
        the graph content (nodes and edge weights)?}
}

\newglossaryentry{RQ3}
{
  %
  name={\textbf{RQ3}},
  %
  description={is it possible to accurately predict swarm behavior
      across different non-trivial scenarios using a single model which captures
      underlying behavioral dynamics?}  }

\newglossaryentry{RQ3.1}
{
  %
  name={\textbf{RQ3.1}},
  %
  description={ can non-linear behavioral dynamics be captured using
      linear modeling?  } }

\newglossaryentry{RQ3.2} {
  %
  name={\textbf{RQ3.2}},
  %
  description={can behavioral dynamics in the be comprehensively captured using
    linear model which is derived directly from first principles (e.g., swarm
    density, swarm size, robot control algorithm), rather than relying on
    post-hoc model fitting?}  }

\newglossaryentry{RQ4}
{
  %
  name={\textbf{RQ4}},
  %
  description={under what conditions are precise, provable guarantees of
      collective and individual behaviors possible in robot swarms?}
}
